Neuroanatomical priors improve image-based cortical thickness computation: ROI-DiReCT

### 2015-10-21 manuscript.tex
introduction

Working memory is a temporal process to maintain and manipulate information over short periods of time. WM has been shown to be impaired in many neurological and psychiatric syndromes including Schizophrenia. It was thought to be tightly associated with cognitive deficits in Schizophrenia. WM itself is a complex process which has been multidimensionally related to the psychosis.

@@

>>>>

Working memory is a temporal process to maintain and manipulate information over short periods of time. WM has been shown to be impaired in many neurological and psychiatric syndromes including Schizophrenia. It was thought to be tightly associated with cognitive deficits in Schizophrenia (Green 2000). WM itself is a complex process which has been multidimensionally related to the psychosis.

@@

Schizophrenia has often been conceived as a disorder of connectivity between components of large-scale brain networks(Lynall, 2010). A few studies has focused on the relationship between WM impairment and disturbed functional connectivity both in the resting state and under various task. Some imagining studies reporting altered 
patterns of interregional functional connectivity in patients with schizophrenia during working memory task performance (Meyer-Lindenberg et al., 2001; Quintana et al., 2003; Schlosser et al., 2003a; Whalley et al., 2005). However, seldomly studies have investigate the functional connectivity in resting state.
